### 2013-03-21 inst/examples/pomp-example.Rmd
pomp example updated with iterated filtering

```{r}
theta <- c(r = 0.75, K = 10, Q = 3, H = 1, a = 1.3, 
           sigma = 0.2, tau = 0.1, X.0 = 5) 
```
```

@@

```{r}
theta.guess <- theta + abs(rnorm(length(theta)))
estpars <- names(theta) # which pars should be estimated. lets try and get them all
rw.sd <- theta/(50*theta) # a named vector of random walk values. This sets it to 0.02 for all pars
system.time(mf <- 
  mif(may, Nmif = 100, # Number of iterations
      start = theta.guess, # Starting value of parameters
      transform = TRUE, # work in transformed parameter space (e.g. log to avoid negative par values)
      pars = estpars,  # which parameters to estimate (others fixed at starting value)
      rw.sd = rw.sd, # random walk width
      Np = 2000, # Number of particles
      var.factor = 4, # scaling factor for random walk sd
      ic.lag = 10, # fixed lag
      cooling.factor = 0.999, # exponential cooling
      max.fail = 10) # internal tolerance
)
```

>>>>

```{r}
theta <- c(r = 0.75, K = 10, Q = 3, H = 1, a = 1.3, 
           sigma = 0.2, tau = 0.1, X.0 = 5) 
```

@@

```{r}
theta.guess <- theta + c(abs(rnorm(length(theta)-1)),0)
estpars <- names(theta[1:7]) # which pars should be estimated. lets try and get them all
rw.sd <- theta[1:7]/(50*theta[1:7]) # a named vector of random walk values. This sets it to 0.02 for all pars
system.time(mf <- 
  mif(may, Nmif = 10, # Number of iterations
      start = theta.guess, # Starting value of parameters
      transform = TRUE, # work in transformed parameter space (e.g. logs avoid neg par values)
      pars = estpars,  # which parameters to estimate (others fixed at starting value)
      rw.sd = rw.sd, # random walk width
      Np = 200, # Number of particles
      var.factor = 4, # scaling factor for random walk sd
      ic.lag = 10, # fixed lag
      cooling.factor = 0.999, # exponential cooling
      max.fail = 10) # internal tolerance
)
```
